FictionEro - Affective Impact of Fiction

### 2025-12-12 analysis/analysis.qmd
Update analysis.qmd
Added ZOIB arousal models (combined mdoels)

```{r}
arousal1 <- readRDS("models/ModelArousal_1.rds")
arousal2 <- readRDS("models/ModelArousal_2.rds")
```

@@

@@

```{r}
draft_model <- brms::brm(
  formula = Arousal ~ Gender / (Condition * ConditionBelief) + (1  + Condition | Participant) + (1|Item),
  data = df2,
  algorithm = "meanfield",
  family = brms::zero_one_inflated_beta())

g1 <- modelbased::estimate_grouplevel(draft_model)

# saveRDS(g1, file = "draft_model_estimates.rds")

@@

```{r}
# g1 <- readRDS("draft_model_estimates.rds")

table_dvour(g1)

>>>>

```{r}
arousal1_GAU <- readRDS("models/Gaussian/ModelArousal_1.rds")
arousal2_GAU <- readRDS("models/Gaussian/ModelArousal_2.rds")

arousal1_ZOIB <- readRDS("models/ZOIB/ModelArousal_1_ZOIB.rds")
arousal2_ZOIB <- readRDS("models/ZOIB/ModelArousal_2_ZOIB.rds")
```

@@

```{r}
params_table(arousal1_ZOIB)
summary(arousal1_ZOIB, robust = TRUE)
```

```{r}
params_table(arousal2_ZOIB) 
summary(arousal2_ZOIB, robust = TRUE)
```

@@

```{r}
a1 <- modelbased::estimate_grouplevel(arousal1)
a2 <- modelbased::estimate_grouplevel(arousal2)

@@

```{r}
table_dvour(a2)
```
